---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Coverage Status](https://img.shields.io/codecov/c/github/ColinFay/tidystringdist/master.svg)](https://codecov.io/github/ColinFay/tidystringdist?branch=master)

[![Travis-CI Build Status](https://travis-ci.org/ColinFay/tidystringdist.svg?branch=master)](https://travis-ci.org/ColinFay/tidystringdist)


# tidystringdist

Compute string distance the tidy way. Built on top of the `stringdist` package.

## Install tidystringdist

You'll get the dev version on: 

```{r eval = FALSE}
devtools::install_github("ColinFay/tidystringdist")
```

Stable version is available with : 

```{r eval = FALSE}
install.packages("tidystringdist")
```


## tidystringdist basic workflow

## tidycomb 

First, you need to create a tibble with the combinations of words you want to compare. You can do this with the `tidy_comb` and `tidy_comb_all` functions. The first takes a base word and combines it with each elements of a list or a column of a data.frame, the 2nd combines all the possible couples from a list or a column.

If you already have a data.frame with two columns containing the strings to compare, you can skip this part. 

```{r}
library(tidystringdist)

tidy_comb_all(LETTERS[1:3])
```

```{r}
tidy_comb_all(iris, Species)
```


```{r}
tidy_comb("Paris", state.name[1:3])
```

### tidy_string_dist

Once you've got this data.frame, you can use `tidy_string_dist` to compute string distance. This function takes a data.frame, the two columns containing the strings, and a stringdist method. 

Note that if you've used the `tidy_comb` function to create your data.frame, you won't need to set the column names. 

```{r example, warnings = FALSE, error=FALSE, message=FALSE}
library(dplyr)
data(starwars)
tidy_comb_sw <- tidy_comb_all(starwars, name)
tidy_stringdist(tidy_comb_sw)
```

Default call compute all the methods. You can use specific method with the `method` argument: 

```{r}
tidy_stringdist(tidy_comb_sw, method = c("osa","jw"))
```

## Tidyverse workflow

The goal is to provide a convenient interface to work with other tools from the tidyverse. 

```{r}
tidy_stringdist(tidy_comb_sw, method= "osa") %>%
  filter(osa > 20) %>%
  arrange(desc(osa))
```

```{r}
starwars %>%
  filter(species == "Droid") %>%
  tidy_comb_all(name) %>%
  tidy_stringdist() %>% 
  summarise_if(is.numeric, mean)
```

### Contact

Questions and feedbacks [welcome](mailto:contact@colinfay.me)!
